---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# watcher

<!-- badges: start -->
[![R-CMD-check](https://github.com/shikokuchuo/watcher/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/shikokuchuo/watcher/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/shikokuchuo/watcher/graph/badge.svg)](https://app.codecov.io/gh/shikokuchuo/watcher)
<!-- badges: end -->

Watch the File System for Changes

R binding for 'libfswatch', a filesystem monitoring library.

All functions are asynchronous and do not block your session.

- Set watches on files or directories recursively.
- Log activity, or trigger an R function to run when a specified event occurs.

## Installation

You can install the development version of watcher from:

``` r
pak::pak("shikokuchuo/watcher")
```

## Example

Create a 'watch' using `watcher::watcher()`.

By default this will watch your current working directory recursively and write events to `stdout`.

Set the `callback` argument to run an arbitrary R function every time an event triggers. This uses the `later` package to execute the callback when R is idle at the top level, or whenever `later::run_now()` is called, for example automatically as part of Shiny's event loop.

```{r example}
library(watcher)
dir <- file.path(tempdir(), "watcher-example")
dir.create(dir)

w <- watcher(dir, recursive = TRUE, callback = function() print("event triggered"))

watcher_start(w)
Sys.sleep(1L)
file.create(file.path(dir, "oldfile"))
later::run_now(2L)
file.rename(file.path(dir, "oldfile"), file.path(dir, "newfile"))
later::run_now(2L)
file.remove(file.path(dir, "newfile"))
later::run_now(2L)
watcher_stop(w)

unlink(dir, force = TRUE)
```
